Unimodular covers of 3-dimensional parallelepipeds and Cayley sums

### 2019-07-13 unimodular-covers.tex
checking comments

\paco{define mixed IDP, Cayley sums, Minkowski sums, mixed subdivisions in the intro? Probably not}
A lattice polytope is called \emph{smooth} if it is simple and the edge generators at every vertex form a linear basis for the lattice. 
%
Oda~\cite{Oda1997} posed several questions regarding smoothness and IDP for lattice polytopes. The following versions of them are now considered conjectures~\cite{HNPS2008,mfo2007}:
\begin{conjecture}
\label{conj:Oda}
\begin{enumerate}
\item 
\label{itm:smoothIDP}
(Related to problems 2 and 5 in \cite{Oda1997})
Every smooth lattice polytope is IDP.
\item 
\label{itm:mixedIDP}
(Related to problems 1, 3, 4, 6 in \cite{Oda1997}) Let $P, Q\subset \R^d$ be lattice polytopes with the normal fan of $P$ refining that of $Q$, and $Q$ smooth. Then
\begin{align*}
\label{eq:mixedIDP}
(P+Q) \cap \Z^d = P \cap \Z^d + Q \cap \Z^d.
\end{align*}

The condition that the normal fan of $Q$ is finer than that of $P$ is sometimes dubbed \emph{$P$ is a weak Minkowski summand of $Q$}, since it is equivalent to the existence of a polytope $P'$ such that $P+P' = k Q$ for some dilation constant $k>0$~\cite[??]{Grunbaum}. 
It has the following algebraic implication for the projective toric variety $X_Q$ corresponding to (the normal fan of) $Q$: $P$ is a weak Minkowski summand of $Q$ if and only if the corresponding Cartier divisor $D_P$ on  $X_Q$ is \emph{numerically effective}, or ``nef''~\cite[Cor.~6.2.15, Prop.~6.3.12]{CLS}; (observe that~\cite{CLS} use ``Minkowski summand'' meaning what we call ``weak Minkowski summand''). 
\paco{added this explanation}
\end{enumerate}
\end{conjecture}

>>>>

A lattice polytope is called \emph{smooth} if it is simple and the edge generators at every vertex form a linear basis for the lattice. 
%
Oda~\cite{Oda1997} posed several questions regarding smoothness and IDP for lattice polytopes. The following versions of them are now considered conjectures~\cite{HNPS2008,mfo2007}:
\begin{conjecture}
\label{conj:Oda}
\begin{enumerate}
\item 
\label{itm:smoothIDP}
(Related to problems 2 and 5 in \cite{Oda1997})
Every smooth lattice polytope is IDP.
\item 
\label{itm:mixedIDP}
(Related to problems 1, 3, 4, 6 in \cite{Oda1997}) Let $P, Q\subset \R^d$ be lattice polytopes with the normal fan of $P$ refining that of $Q$, and $Q$ smooth. Then
\begin{align*}
\label{eq:mixedIDP}
(P+Q) \cap \Z^d = P \cap \Z^d + Q \cap \Z^d.
\end{align*}
\end{enumerate}
\end{conjecture}

Motivated by  \Cref{conj:Oda}\eqref{itm:mixedIDP}, we recall the following definitions:

\begin{definition}
We say that $P$ is a weak Minkowski summand of $Q$ if the normal fan of $Q$ refines that of $P$.
\end{definition}
The name is due to the fact that the condition on the refinement of the normal fans is equivalent to the existence of a polytope $P'$ such that $P+P' = k Q$ for some dilation constant $k>0$~\cite[??]{Grunbaum}. 
It has the following algebraic implication for the projective toric variety $X_Q$ corresponding to (the normal fan of) $Q$: $P$ is a weak Minkowski summand of $Q$ if and only if the corresponding Cartier divisor $D_P$ on  $X_Q$ is \emph{numerically effective}, or ``nef''~\cite[Cor.~6.2.15, Prop.~6.3.12]{CLS}; (observe that~\cite{CLS} use ``Minkowski summand'' meaning what we call ``weak Minkowski summand''). 
\paco{added this explanation}

\begin{definition}
The pair $(P, Q)$ has the integer decomposition property, or is IDP, if 
\begin{align*}
(P+Q) \cap \Z^d = P \cap \Z^d + Q \cap \Z^d.
\end{align*}
\end{definition}

In this language,  \Cref{conj:Oda}\eqref{itm:mixedIDP} can be rephrased as if $P$ is a weak Minkowski summand of $Q$ and $Q$ is smooth, then the pair $(P,Q)$ is IDP.
